### 2022-10-19 draft/draft.Rmd
almost done

\section*{Appendix A: Proofs of Theorems}

@@

@@

The statement of the theorem assumes that for each community $k$, there at least $R + 1$ points with known label $k$. 
For simplicity, suppose we have exactly $R + 1$ (if there are more, then discard the rest). 
Then for each community $k$, it is possible to fit a polynomial of order $R$ that goes through each of the $R + 1$ known points exactly (see appendix B), yielding $g(t; \hat{p}_k)$, where $\hat{p}_k$ are the fitted coefficients of the Bezier polynomial. 
Use the fitted Bezier curves to define $\delta_k(t) = \|Q g(t; \hat{p}_k) - g(t; p_k)\|$, $\delta_k = \max_t \delta_k(t)$, and $\delta = \max_k \delta_k$. 
Since $P(\epsilon < M n^{-1/2} \log^c n) \to 1$ for constants $M, c > 0$, 
$P(\delta_k < M n^{-1/2} \log^c n) \to 1$ for each $k$. 
Since $\epsilon_i$ describes the error between each embedding point and its corresponding latent vertex, and $\delta_k(t_i)$ describes the error between the fitted curve and its corresponding true curve in the latent space, 
$L < \frac{1}{n} \sum_i \epsilon_i + \delta_{z_i}(t_i) < \frac{1}{n} n (\epsilon + \delta) = \epsilon + \delta$. 
Then $P(L < 2 M n^{-1/2} \log^c n) > P(\epsilon + \delta < 2 M n^{-1/2} \log^c n) \to 1$ as $n \to \infty$.

@@

\section*{Appendix B: Details on Fitting Bezier Curves to Noisy Data}

@@

\section*{Appendix C: Supplementary Materials}

>>>>

\section*{Appendix A: Proofs of Theorems from Section 3}

@@

\section*{Appendix B: Proofs of Theorems from Section 4}

@@

The statement of the theorem assumes that for each community $k$, there at least $R + 1$ points with known label $k$. 
For simplicity, suppose we have exactly $R + 1$ (if there are more, then discard the rest). 
Then for each community $k$, it is possible to fit a polynomial of order $R$ that goes through each of the $R + 1$ known points exactly (see appendix C), yielding $g(t; \hat{p}_k)$, where $\hat{p}_k$ are the fitted coefficients of the Bezier polynomial. 
Use the fitted Bezier curves to define $\delta_k(t) = \|Q g(t; \hat{p}_k) - g(t; p_k)\|$, $\delta_k = \max_t \delta_k(t)$, and $\delta = \max_k \delta_k$. 
Since $P(\epsilon < M n^{-1/2} \log^c n) \to 1$ for constants $M, c > 0$, 
$P(\delta_k < M n^{-1/2} \log^c n) \to 1$ for each $k$. 
Since $\epsilon_i$ describes the error between each embedding point and its corresponding latent vertex, and $\delta_k(t_i)$ describes the error between the fitted curve and its corresponding true curve in the latent space, 
$$L < \frac{1}{n} \sum_i \epsilon_i + \delta_{z_i}(t_i) < \frac{1}{n} n (\epsilon + \delta) = \epsilon + \delta.$$ 
Then as $n \to \infty$, 
$$P(L < 2 M n^{-1/2} \log^c n) > P(\epsilon + \delta < 2 M n^{-1/2} \log^c n) \to 1.$$

@@

\section*{Appendix C: Details on Fitting Bezier Curves to Noisy Data}

@@
